\begin{rubric}{Projects}
\noentry{~}

\entry*[Medical LV Segmentation]
U-Net for left-ventricle segmentation on Stanford EchoNet-Dynamic; compared pixel-wise masks vs. landmark detection; used Dice score and morphology post-processing.\hfill \smallcaps{Tech:} PyTorch, OpenCV, Albumentations\hfill \smallcaps{Link:} \url{https://github.com/Tec-AI-23/EchoNetDynamic}

\entry*[Human Activity Recognition]
Evaluated 18 ML algorithms with grid search on accelerometer data to classify activity levels in older adults; validated via CV and significance tests.\hfill \smallcaps{Link:} \url{https://github.com/Tec-AI-23/HAR70}

\entry*[Hydrological Forecasting]
Deep CNN pipeline predicting river stage from imagery; EfficientNet transfer learning and multi-modal inputs (visual + hydrological) for accuracy gains.\hfill \smallcaps{Link:} \url{https://github.com/musel25/research_deep_learning}

\entry*[LLM + RAG for Metaheuristics]
Automated framework using RAG + LLMs to generate and refine metaheuristics for black-box optimisation; integrated Qwen2.5-coder, ChromaDB, and Optuna.\hfill \smallcaps{Link:} \url{https://github.com/musel25/llm-metaheuristics}

\entry*[Obesity Level Estimation]
End-to-end classification on UCI obesity dataset; DR (PCA, t-SNE), mutual information, 31 models; best: XGBoost (96\%).\hfill \smallcaps{Link:} \url{https://github.com/musel25/obesity_ml}

\entry*[Leukocyte CNN + LIME]
CNN to classify leukocytes (cancerous vs non-cancerous) with LIME explanations to highlight decision-driving regions.

\entry*[Fine-tuned GPT-2 Chatbot]
Fine-tuned GPT-2 on WhatsApp chats; regex parsing to HF Datasets; trained and deployed interactive chatbot pipeline.\hfill \smallcaps{Link:} \url{https://github.com/musel25/her_if_it_was_2025}

\entry*[NLP Web App]
Real-time text emotion classifier with logging and analytics; built using Streamlit and standard NLP preprocessing.\hfill \smallcaps{Link:} \url{https://github.com/musel25/nlp_project}

\end{rubric}

